### 2025-01-15 NLP/exercises.tex
Small update.

  \begin{solution}
    \begin{enumerate}
      \item \begin{itemize}
          \item \textbf{Engine A}:
            \begin{itemize}
              \item $P@5 = \frac{3}{5} = .6$
              \item $P@10 = \frac{7}{10} = .7$
              \item $MA@5 = (\frac{1}{1} + \frac{2}{3} + \frac{3}{5}) / 3 = .756$
            \end{itemize}
          \item \textbf{Engine B}:
            \begin{itemize}
              \item $P@5 = \frac{1}{5} = .2$
              \item $P@10 = \frac{4}{10} = .4$
              \item $MAP@5 = (\frac{1}{4}) / 1 = .25$
            \end{itemize}
        \end{itemize}
      \item These metrics help evaluate IR systems by measuring precision at different cutoff points and the average precision across all relevant documents.
    \end{enumerate}
  \end{solution}
\end{exercise}

@@

  \begin{solution}
    \begin{itemize}
        \item \textbf{Reducing filters}: Remove restrictive criteria (e.g., date, location).
        \item \textbf{Boosting document recall}: Index more documents or reduce relevance thresholds.

    \end{itemize}
  \end{solution}
\end{exercise}

@@

\begin{exercise}{TREC}\label{ex:trec}
  What are the TREC question types?

  \begin{solution}
    \begin{itemize}
        \item \textbf{Factoid questions}: Require specific factual answers (e.g., "Who is the president of the U.S.?").
        \item \textbf{List questions}: Require a list of items (e.g., "What countries are in the EU?").
        \item \textbf{Definition questions}: Seek explanations or definitions (e.g., "What is AI?").
    \end{itemize}
  \end{solution}
\end{exercise}

>>>>

  \begin{solution}
    \begin{enumerate}
      \item \begin{itemize}
          \item \textbf{Engine A}:
            \begin{itemize}
              \item $P@5 = \frac{3}{5} = .6$
              \item $P@10 = \frac{7}{10} = .7$
              \item $MAP@5 = (\frac{1}{1} + \frac{2}{3} + \frac{3}{5}) / 3 = .756$
            \end{itemize}
          \item \textbf{Engine B}:
            \begin{itemize}
              \item $P@5 = \frac{1}{5} = .2$
              \item $P@10 = \frac{4}{10} = .4$
              \item $MAP@5 = (\frac{1}{4}) / 1 = .25$
            \end{itemize}
        \end{itemize}
      \item These metrics help evaluate IR systems by measuring precision at different cutoff points and the average precision across all relevant documents.
    \end{enumerate}
  \end{solution}
\end{exercise}

@@

  \begin{solution}
    \begin{itemize}
        \item \textbf{Reducing filters}: Remove restrictive criteria (e.g., date, location).
        \item \textbf{Boosting document recall}: Index more documents or reduce relevance thresholds.
    \end{itemize}
  \end{solution}
\end{exercise}

@@

\begin{exercise}{TREC}\label{ex:trec}
  What are the 6 TREC question types?

  \begin{solution}
    Abbreviation, Entity, Description, Human, Location, Numeric.
  \end{solution}
\end{exercise}
